Enriching Object Detection with 2D-3D Registration\\and Continuous Viewpoint Estimation

### 2015-01-20 rebuttal/rebuttal.md

We appreciate the valuable comments from all the reviewers. We are happy to
hear RWs agree that we address a

The paper present major improvements to the WHO approach (speed and performance) by thoroughly analyzing exisitn gWHO and performed extensive experiments to validate as pointed by [R1] and

# Weakness

## Scalability [R1]

This gives the user degree of accuracy they aim

## Realistic Textured Model as oppose to Simple Geometric Model

## Effectiveness of Fine Tuning [R1]

This gives the user degree of accuracy they aim

## Limited PASCAL 3D+ Experiments

- This is a good dataset to report results in pose estimation, and improving
  the baseline is one of the strength of the paper. However, the strength of
  the dataset is that it has more than 10 categories: why report results only
  on cars and bicycles?[R2]

Another good thing about this approach is that it can augment the output of 2D detectors which is very valuable.[R1]

## Writing [R2]

As [R2] pointed out, we thank [R2] for pointing out missing references. The final version will not have any writing issues.

# Ambiguity

## Calibration, Inversion one time process?

almost 4 seconds for original WHO computation seems very bad. From the text, it seems to me that the authors considered the time of the inversion of Sigma. Since it can be done only once (or downloaded from internet) there is no reason to consider it! Also, a fair comparison would consider a GPU implementation of the (sparse) matrix product involved, and that would probably be extremely fast as well [R2]

Rebuttal : The matrix $\Sigma \in \mathcal{R}^{(W\times H\times F) \times (W\times H\times F)}$ where $W$ is the number of HOG cells in width and $H$ is the number of HOG cells in the height and $F$ is the number of features which is 31 for HOG. Usually, the sigma matrix is about $7000 \times 7000$ for a specific template size and if you save it as a 4Byte double this takes 180MByte which is prohibitive. Not only the matrix is aspect ratio specific, but it also is specific for foreground mask. Our approach, which we experimentally validated, decorrelates only the foreground thus requires foreground mask specific sigma. Thus there is no way to cache/download the large matrix sigma. The other reviews [R1, R3] considered as a great improvement over WHO feature. The matrix is very dens due to the fact that the lines are usually continuous. All templates have different aspect ratio which cannot be cached nor downloadable. The inversion is unique for each template. We will emphasize  this point in the final paper.

## Variation of WHO.

almost 4 seconds for original WHO computation seems very bad. From the text, it seems to me that the authors considered the time of the inversion of Sigma. Since it can be done only once (or downloaded from internet) there is no reason to consider it! Also, a fair comparison would consider a GPU implementation of the (sparse) matrix product involved, and that would probably be extremely fast as well [R2]
Rebuttal : All templates have different aspect ratio which cannot be cached nor downloadable. The inversion is unique for each template.
analyzing the existing WHO approach and suggesting improvements to it. The authors have performed extensive experiments to validate their approach, comparing against all variations of WHO and justifying their insights. I think this part of the work is very well done. The proposed method shows considerable improvement over the existing state of the art techniques. It is much simpler to understand and optimize than existing techniques which is an added advantage. [R1]

### 2015-01-22 rebuttal/rebuttal.md

We appreciate the valuable comments from all the reviewers. We are happy to
hear reviewers agree that we proposed “efficient”[R2,R3] and “considerable
improvements to WHO”[R1] in terms of “speed”[R1,R3] and “detection
performance”[R1]. The method was “well motivated”  was validated with
“extensive experiments”[R1].

R1.1 & [R2 one-time]: Our method proposed a way to fine tune the viewpoint in
continuous space without expensive training thus providing vision community a
modular framework for view estimation. However, caching all possible templates
would be intractable and difficult to cover continuous azimuth, elevation,
in-plane rotation, focal length and intraclass CAD models. To overcome, our
method generates proposals on-the-fly which requires covariance inversion which
we handled by Conjugate Gradient.

R1 & R2, effectiveness of fine-tuning: The continuous viewpoint estimation not
only recovers from wrong pose but also accurately refine the viewpoint.
Unfortunately, the PASCAL 3D+ and 3D Object datasets only measures the number
of correct viewpoint bins from bird-eye view. If a viewpoint estimation fall
into the correct bin in the coarse estimation, the improvement from the
fine-tuning cannot be measured. So the improvements comes from the fine-tuning
measured using the criteria is the number of recovers from wrong initialization
only. We will explain this point in our final paper.

R1, RCNN + Ours: DPM-VOC+VP method templates are made from ground truth
bounding boxes so the bounding boxes are more tight and informative compare to
region based bounding boxes (RCNN). Our algorithm tries to handle such
incorrect bounding boxes by creating HOG scale pyramid for the given bounding
box but more accurate the bounding box is, better the performance. This effect
is dominant for coarser viewpoint where RCNN and DPM-VOC+VP have similar
performance.

R2, inversion time: Sigma is a covariance matrix of size (W x H x F) x (W x H x
F) where W and H are the number of HOG cells in a row and a column, F is the
dimension of HOG feature [Hariharan et al. 12]. In practice, we used
high-resolution template and the resulting covariance matrix was around
7000x7000 (~180MByte in single precision). Thus, using the Cholesky
decomposition, it took more than 4 seconds on i7-4770K. To get extra speed up,
we also tried to make use of the Toeplitz-Block-Toeplitz structure and achieved
O(n log n) time complexity using DFT but the time complexity coefficient was
too large and the non-zero pattern destroys the Toeplitz structure so we did
not incorporated in our paper. We did not emphasize this point in detail
[Sec.4] but will try to incorporate this point in the final version.

Second point raised by [R2] is that the sigma matrix product can be done in GPU
implementation. We think the reviewer meant matrix decomposition since we
compared the matrix inversion time. We thank [R2] for correctly pointing this
out and we will incorporate GPU implementation of Cholesky decomposition
experiment in our final paper.

R3, Zia el al.: We thank the reviewer for point this out. We agree that Zia et
al. tackles the similar problem. However, due to their complex model, their
model requires accurate bounding box and viewpoint estimation. On the other
hand, our method can work as a standalone detector and performs on par with
many state-of-the-art detectors though the dataset is saturated as correctly
pointed by [R1]. But we think this is a good comparison and we will add
discussion and comparison with Zia et al on the final version.

We thank R2 for pointing out writing errors and missing references. Although
our article is “well written”[R1] and “explains ... well”[R1], we also noticed
the errors and fixed them including the ones pointed out by R2. We apologize
for such mistakes.

We will try our best to incorporate all the remaining issues pointed out by the
reviewers to the final paper should it be accepted.

### 2015-01-22 rebuttal/rebuttal.md

We appreciate the valuable comments from all the reviewers. We are happy to
hear reviewers agree on that we proposed “efficient”[R2,R3] and “considerable
improvements to WHO”[R1] in terms of “speed”[R1,R3] and “detection
performance”[R1]. The method was “well motivated”  and validated with
“extensive experiments”[R1].

R1.1 & [R2 one-time]: Our method proposed a way to fine tune the viewpoint in
continuous space without expensive training thus providing vision community a
modular framework for view estimation. However, caching all possible templates
would be intractable and difficult to cover all continuous azimuth, elevation,
in-plane rotation, focal length and intraclass CAD models. To overcome, our
method generates proposals on-the-fly which requires covariance inversion.

R1 & R2, effectiveness of fine-tuning: The continuous viewpoint estimation not
only recovers from wrong pose but also accurately refines the coarse viewpoint estimation.
Unfortunately, the PASCAL 3D+ and 3D Object datasets only measures the number
of correct viewpoint bins from bird-eye view. If a viewpoint estimation falls
into the correct bin in the coarse estimation, the improvement from the
fine-tuning cannot be measured using the metric. So the improvements come 
measured using the criteria is the number of viewpoint recovery from grossly wrong estimation 
only. This point was not explicit in the paper so we will add this point in our final paper.

R1, RCNN + Ours: DPM-VOC+VP method templates were made from ground truth
bounding boxes so the bounding boxes tend to be tighter and more informative than
the region based bounding boxes (RCNN). Our algorithm handles over/under 
estimated bounding boxes by creating HOG scale pyramid but more accurate 
the bounding box is, the better the performance. This effect
is dominant for coarser viewpoint where RCNN and DPM-VOC+VP have similar
detection performance.

R2, inversion time: Sigma is a covariance matrix of size (W x H x F) x (W x H x
F) where W and H are the number of HOG cells in a row and a column, F is the
dimension of HOG feature [Hariharan et al. 12]. In practice, we used
high-resolution template and the resulting covariance matrix was around
7000x7000 (~180MByte in single precision). Thus, using the Cholesky
decomposition, it took more than 4 seconds on i7-4770K. To get extra speed up,
we also tried to make use of the Toeplitz-Block-Toeplitz structure and achieved
O(n log n) time complexity using DFT but the time complexity coefficient was
too large and the non-zero pattern destroys the Toeplitz structure. We 
did not fully explained the size of the matrix [Sec.4] but will try to 
incorporate this point in the final version.

@@

Second point raised by [R2] is that the sigma matrix product can be done in GPU
implementation. We think the reviewer meant matrix decomposition since we
compared the matrix inversion time. We thank [R2] for correctly pointing this
out and we will incorporate GPU implementation of Cholesky decomposition
experiment in our final paper.

R3, Zia el al.: We thank the reviewer for pointing this out. We agree that Zia et
al. tackles the similar problem. However, due to the complexity, their
model requires accurate bounding box as well as viewpoint estimation as an 
initialization. On the other hand, our method can work as a standalone detector 
and performs on par with many state-of-the-art detectors on the 3D Object dataset
though the dataset is saturated as correctly pointed out by [R1]. But we think 
this is a good comparison and we will add comparison with Zia et al on the final version.

We thank R2 for pointing out writing errors and missing references. Although
our article is “well written”[R1] and “explains ... well”[R1], there were slipped errors
which we fixed them including the ones pointed out by R2. We apologize
for such mistakes.

### 2015-01-22 rebuttal/rebuttal.md

We appreciate the valuable comments from all the reviewers. We are happy to
hear reviewers agree on that we proposed “efficient”[R2,R3] and “considerable
improvements to WHO”[R1] in terms of “speed”[R1,R3] and “detection
performance”[R1]. The method was “well motivated”  and validated with
“extensive experiments”[R1].

Caching Sigma inverse for the templates [R1, R2]: 
We propose a way to fine tune the viewpoint in
continuous space without expensive training, thus providing the vision community
with a modular framework for viewpoint estimation. However, caching all the possible
templates for continuous azimuth, elevation, in-plane rotation, focal length and
intraclass CAD models is intractable. To overcome this, our
method generates proposals on-the-fly which requires covariance inversion.

Effectiveness of fine-tuning [R1, R2]:
Our continuous viewpoint estimation method not only accurately refines the coarse
viewpoint estimation but also recovers from incorrect pose initializations.
Unfortunately, the PASCAL 3D+ and 3D Object datasets only measure the number
of correct viewpoint bins from bird-eye view. If the coarse viewpoint estimation
falls into the correct bin, we cannot observe further refinement using this metric.
Therefore, the improvements we present only represent the refinement of poses that
are initially estimated incorrectly.
This point was not explicit in the paper abd we will add it to our final paper.

@@

R1, RCNN + Ours: DPM-VOC+VP method templates were made from ground truth
bounding boxes so the bounding boxes tend to be tighter and more informative than
the region based bounding boxes (RCNN). Our algorithm handles over/under 
estimated bounding boxes by creating HOG scale pyramid but more accurate 
the bounding box is, the better the performance. This effect
is dominant for coarser viewpoint where RCNN and DPM-VOC+VP have similar
detection performance.

Sigma inversion time [R2]:
Sigma is a covariance matrix of size (W x H x F) x (W x H x F)
where W and H are the number of HOG cells in a row and a column, and F is the
dimension of HOG feature [Hariharan et al. 12]. In practice, we used
high-resolution template and the resulting covariance matrix was around
7000x7000 (~180MByte in single precision). Thus, using the Cholesky
decomposition, it took more than 4 seconds on i7-4770K. To get extra speed up,
we also tried to make use of the Toeplitz-Block-Toeplitz structure and achieved
O(n log n) time complexity using DFT but the time complexity coefficient was
too large and the non-zero pattern destroys the Toeplitz structure. We 
did not fully explain the size of the matrix [Sec.4] but will
incorporate this point in the final version.

The second point raised by [R2] is that the sigma matrix product can be done in GPU
implementation. We think the reviewer meant matrix decomposition since we
compared the matrix inversion time. We thank [R2] for correctly pointing this
out and we will incorporate a GPU implementation of the Cholesky decomposition
experiment in our final paper.

Related work from Zia el al. [R3]:
We thank the reviewer for pointing this out. We agree that Zia et
al. tackles the similar problem. However, due to the complexity, their
model requires accurate bounding box as well as viewpoint estimation as an 
initialization. On the other hand, our method can work as a standalone detector 
and performs on par with many state-of-the-art detectors on the 3D Object dataset
(though the dataset is saturated as correctly pointed out by [R1]).
We will add comparison with Zia et al on the final version.

We thank [R2] for pointing out writing errors and missing references. Although
our article is “well written” [R1] and “explains ... well” [R1], some minor errors
slipped through, which will of course be fixed in the final version.
We apologize for such mistakes.

We will try our best to incorporate all the remaining issues pointed out by the
reviewers in the final paper should it be accepted.

### 2015-01-23 rebuttal/rebuttal.md

We appreciate the valuable comments from all the reviewers. We are happy to
hear reviewers agree on that we proposed “efficient”[R2,R3] and “considerable
improvements to WHO”[R1] in terms of “speed”[R1,R3] and “detection
performance”[R1]. The method was “well motivated”  and validated with
“extensive experiments”[R1].

One-time calibration [R1, R2]: We propose a way to fine tune the viewpoint in
continuous space without expensive training, thus providing the vision community
with a modular framework for viewpoint estimation. However, caching all the possible
templates for continuous azimuth, elevation, in-plane rotation, focal length and
intraclass CAD models is intractable. To overcome this, our
method generates proposals on-the-fly which requires covariance inversion on-the-fly.

Effectiveness of fine-tuning [R1, R2]: Our continuous viewpoint estimation
method not only accurately refines the coarse
viewpoint estimation but also recovers from incorrect pose initializations.
Unfortunately, the PASCAL 3D+ and 3D Object datasets only measure the number
of correct viewpoint bins from bird-eye view. If the coarse viewpoint estimation
falls into the correct bin, we cannot observe further refinement using this metric.
Therefore, the improvements only represent the recovery of poses that
are initially estimated incorrectly.
This point was not explicit in the paper and we will add it to our final paper.

RCNN + Ours [R1]: DPM-VOC+VP method templates were made from ground truth
bounding boxes so the bounding boxes tend to be tighter and more informative than
the region based bounding boxes (RCNN). Our algorithm handles over/under 
estimated bounding boxes by creating HOG scale pyramid but more accurate 
the bounding box is, the better the performance. This effect
is dominant for coarser viewpoint where RCNN and DPM-VOC+VP have similar
detection performance.

### 2015-01-23 rebuttal/rebuttal.md

We appreciate the valuable comments from all the reviewers. We are happy to
hear reviewers agree on that we proposed “efficient”[R2,R3] and “considerable
improvements to WHO”[R1] in terms of “speed”[R1,R3] and “detection
performance”[R1]. The method was “well motivated”  and validated with
“extensive experiments”[R1].

One-time calibration [R1, R2]: We propose a way to fine tune the viewpoint in
continuous space without expensive training, thus providing the vision community
with a modular framework for viewpoint estimation. However, caching 
templates for continuous azimuths, elevations, in-plane rotations, focal lengths and
intraclass CAD models is intractable. To overcome this, our
method generates templates on-the-fly which requires covariance inversion on-the-fly.

Effectiveness of fine-tuning [R1, R2]: Our continuous viewpoint estimation
method not only accurately refines the coarse
viewpoint estimation but also recovers from incorrect pose initializations.
Unfortunately, the PASCAL 3D+ and 3D Object datasets only measure the number
of correct viewpoint bins from a bird’s-eye view. If the coarse viewpoint estimation
falls into the correct bin, we cannot observe further refinement using this metric.
Therefore, the improvements only represent the recoveries of poses from
grossly wrong estimations.
This point was not explicit in the paper and we will add it to our final paper.

RCNN + Ours improvements [R1]: DPM-VOC+VP method templates were made from ground truth
bounding boxes, so the bounding boxes tend to be tighter and more informative than
the region-based bounding boxes (RCNN). Our algorithm handles over/under 
estimated bounding boxes by creating HOG scale pyramid but more accurate 
the bounding box is, the better the performance. This effect
is dominant for coarser viewpoint where RCNN and DPM-VOC+VP have similar
detection performance.

Sigma inversion time [R2]: Sigma is a covariance matrix of size (W x H x F) x (W x H x F)
where W and H are the number of HOG cells in a row and a column, and F is the
dimension of HOG feature [Hariharan et al. 12]. In practice, we used
high-resolution templates, resulting in a covariance matrix size of about
7000x7000 (~180MByte in single precision). Thus, using the Cholesky
decomposition, inversion took more than 4 seconds on i7-4770K. To get an extra speed-up,
we also tried to make use of the Toeplitz-Block-Toeplitz structure and achieved
O(n log n) time complexity using DFT but the time complexity coefficient was
too large and the non-zero pattern destroys the Toeplitz structure. We 
did not fully explain the size of the matrix [Sec.4] but will
incorporate this point in the final version.

@@

The second point raised by [R2] is that the sigma matrix product can be done in GPU
implementation. We think the reviewer meant matrix decomposition since we
compared the matrix inversion time. We thank [R2] for correctly pointing this
out and we will incorporate a GPU implementation of the Cholesky decomposition
experiment in our final paper.

Related work from Zia el al. [R3]: We thank the reviewer for pointing this out. We agree that Zia et
al. tackles the similar problem. However, due to the complexity, their
model requires accurate bounding box as well as viewpoint estimation as an 
initialization. On the contrary, our method works also as a standalone detector 
and performs on par with many state-of-the-art detectors on the 3D Object dataset
(though the dataset is saturated as correctly pointed out by [R1]).
We will add comparison with Zia et al on the final version.

@@

We thank [R2] for pointing out writing errors and missing references. Although
our article is “well written” [R1] and “explains ... well” [R1], some minor errors
slipped through, which will of course be fixed in the final version.
We apologize for such mistakes.

We will try our best to incorporate all the remaining issues pointed out by the
reviewers in the final paper should it be accepted.

Total: 3971/4000 Character

----------------------Reviews not incorporated------------------------
From R1
“The work relies on using realistic (with texture) 3D models. This limits the applicability where such rich models are not available.”
“The proposed technique relies on a large number of templates, and their evaluation at many scales.”

From R2
“concerns about the reality of the speed-up” -- do some rough calculation about the naive approach to directly show the speedup of your method
“limited experiments”

From R3
“a little more background on WHO could be given”
“could be tested on KITTI”
“missing baseline”

### 2015-01-26 rebuttal/rebuttal.md

We appreciate the valuable comments from all the reviewers. We are happy to hear reviewers agree on that we proposed “efficient”[R2,R3] and “considerable improvements to WHO”[R1] in terms of “speed”[R1,R3] and “detection performance”[R1]. The method was “well motivated”  and validated with “extensive experiments”[R1].

Contribution & caching templates [R1, R2]: Contribution in our paper is threefold: 1. WHO whitening speedup, 2. bypassing the expensive calibration stage with NZ-WHO, 3. on-the-fly template learning for continuous viewpoint estimation. These novelties enable us to generate rendering and learn calibrated template on-the-fly that makes MCMC procedure tractable. Thus we fine tune the viewpoint in continuous space without expensive training nor calibration, thus providing the vision community with a modular framework for continuous viewpoint estimation. Otherwise it would be intractable to cache and calibrate templates for continuous azimuths, elevations, in-plane rotations, focal lengths and intraclass CAD models.

Effectiveness of fine-tuning [R1, R2]: Our continuous viewpoint estimation method not only accurately refines the coarse viewpoint estimation but also recovers from incorrect pose initializations. Unfortunately, the PASCAL 3D+ and 3D Object datasets only measure the number of correct viewpoint bins from a bird’s-eye view. If the coarse viewpoint estimation falls into the correct bin, we cannot observe further refinement using this metric. Therefore, the improvements only represent the recoveries of poses from grossly wrong estimations.

@@

RCNN + Ours improvements [R1]: DPM-VOC+VP method templates were made from ground truth bounding boxes, so the bounding boxes tend to be tighter and more informative than the region-based bounding boxes (RCNN). Our algorithm handles over/under estimated bounding boxes by creating HOG scale pyramid but more accurate the bounding box is, the better the performance. This effect is dominant for coarser viewpoint where RCNN and DPM-VOC+VP have similar detection performance.

Calibration time [R1]: Yes, the calibration is a one-time process for each template. We followed the standard calibration technique [Aubry 14] and used 200k random negative patches for each template. The method calibrates each template independently.

Sigma inversion time [R2]: To enable on-the-fly template generation, we had to dramatically speed up the covariance inversion time and remove the calibration stage while maintaining the performance. Sigma is a covariance matrix of size (W x H x F) x (W x H x F) [Hariharan et al. 12] and is unique for each aspect ratio and foreground mask [Sec. 4.3]. In practice, we used high-resolution templates, resulting in a covariance matrix size of about 7000x7000 (~180MByte in single precision). Thus, it took ~4 seconds on i7-4770K to inverse matrix using the Cholesky decomposition. Also the sigma matrix is unique for a template size and foreground mask.

The second point raised by [R2] is that the sigma matrix product can be done on GPU. We think the reviewer meant matrix decomposition since matrix product has been done on GPU using FFT and we compared the matrix inversion time only. We thank [R2] for correctly pointing this out and we will incorporate a GPU implementation of the Cholesky decomposition experiment in our final paper.

Related work from Zia et al. [R3]: We thank the reviewer for pointing this out. We agree that Zia et al. tackles the similar problem. However, due to the complexity, their model requires accurate bounding box as well as viewpoint estimation as an initialization. On the contrary, our method works also as a standalone detector and performs on par with many state-of-the-art detectors on the 3D Object dataset (though the dataset is saturated as correctly pointed out by [R1]). We will add comparison with Zia et al on the final version.

2 Classes [R2]: Unlike [Zia et al. PAMI 13](car,bike), [Hejrati el al. CVPR14](car) and [Fidler et al. NIPS12](car,box) we used the car class in PASCAL challenge that varies from a racing car to a truck so the class represents strong intraclass variation. Also, our bicycle class exhibits similar intraclass variability that ranges from three-wheeled bicycles to acrobatic BMX bicycles. We think that the classes are commonly found and real-world applications yet include strong intraclass variability and drastic viewpoints.

Saturated 3D Object [R1]: The AP results reported on Table 2 show some degree of saturation. However MPPE results show that it is still a challenging task and it evaluates the performance fairly since the dataset contains 480 images of cars from various poses and scales. Also the Table 2 has yet another significance that learning from synthetic images can be applied to real images. Also the qualitative results on Figure 7 on the paper and Figure 3. and 4 on the supplementary material are from the dataset and show that our algorithm can actually estimate 3D viewpoint accurately whereas other algorithms can only estimate rough geometry.

@@

We thank [R2] for pointing out writing errors and missing references. Although our article is “well written” [R1] and “explains ... well” [R1], some minor errors slipped through, which will of course be fixed in the final version. We apologize for such mistakes.

We will try our best to incorporate all the remaining issues pointed out by the reviewers in the final paper should it be accepted.

5457/4000 character

-------------------------------------------------------------------------

- R2's comment of lack of novelty: we have to strongly argue against that! we do have plenty of novelty, the most important one being the introduction of the on-the-fly rendering + template learning idea, that makes the MCMC procedure tractable! nobody has done that before!

- R2's concern about the speedup of WHO: 'why do we consider the inversion time at all' is not addressed! I can't see 'almost 4 seconds' in Tab. 1. also, our crucial argument is about the fact that we don't need _calibration_ in order to get good performance, and the speedup w/o considering calibration is not even very relevant?

- R2: we have to argue that making progress on 2 classes is already valuable (and give plenty of references that do that)

- R1's question about 1-time-calibration: is this incorporated in Tab. 1?
that's his question, so 'yes'! also, we have to argue that this in fact _not_ a 1-time-thing, but has to be repeated for templates of different sizes (as they arise all the time in our on-the-fly setting - we don't even know the dimensions beforehand)!

- R1's comment about the significance of the saturated results

### 2015-03-25 approach.tex
Added selector matrix $S$ that generates $x', \mu', \Sigma'$.

We used a public rendering engine to create realistic rendering and
depth. We used CAD models that contain color, texture and material information such as
transparency and reflectance to make the rendering as much realistic
as possible to simulate the natural image statistics. The example rendering is
in Fig. \ref{fig:rendering}. We also extracted depth information as well while
rendering to use in the reconstruction.

We used a collection of CAD models to make exemplar renderings of CAD models and for viewpoints. The
CAD models are cached so that when we fine-tune 2D-3D matching, so it can be rendered instantaneously.
We made the renderings to change focal length and yaw, pitch, roll so that we can fine tune the matching
continuously.

@@

\subsection{Whitened Histograms of Orientations (WHO)}
\label{sec:who}
Our technique for rendering and training template detectors on-the-fly
is drawing from recent work. Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
\cite{Hariharan12}, which uses feature statistics from natural images to whiten HOG
templates, making them more discriminative. Whitening is a common signal
processing operation for decorrelating a set of random variables

\cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
$k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
whitening the signal,
\begin{equation}
\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X]) \label{eq:whitening},
\end{equation}
we remove 2nd order correlation between all features. Since collecting covariance matrix for every template shape
 is expensive, \cite{Hariharan12} proposed easy way to synthesize
covariance $\Sigma$ from autocovariance $\Gamma$ and we followed their
method to generate $\Sigma$.

@@

NZ-WHO removes these artifacts so that the background has no effect on the
template response. Let $T$ be the feature extraction transformation and $p$ be
the rendering setting (see Sect.~\ref{sec:fine}). Given HOG features $x=T(I_r)$
from rendering image $I_r$, we create a new vector $x'$ which
contains only the non-zero elements of $x$. We select the corresponding elements of
$\mu$ to produce $\mu'$, while the autocovariance lookup is only performed for
the cells with non-zero gradient, producing $\Sigma'$ corresponding to the
features in $x'$. After solving the resulting system (which is now smaller than
in the WHO approach) we find

\begin{equation}
w'=\Sigma'^{-1}(x' - \mu') \label{eq:nz-who},
\end{equation}which we reassemble into the final NZ-WHO template $w$ by
replacing the non-zero elements of $x$ with the corresponding $w'$ element.

@@

As a result, a GPU implementation of conjugate gradient converges in 50
ms when using 250 HOG cells, two orders of magnitude faster than the using
Cholesky factorization with Gaussian Elimination.

We report the real time analysis of whitening using decomposition and
conjugate gradient methods in Fig.~\ref{fig:whotime}. (a) compares the
absolute runtime of the different methods while (b) gives the obtained
speedup. We see that % We compare the speed of each of template generation methods in
% Fig.~\cite{fig:covariancetime_crop} Using naive Cholesky decomposition,
WHO template takes several seconds for realistic template sizes of
several hundred cells, while using the iterative Conjugate Gradient
method, it only takes 100ms. If we use NZ-WHO, we can gain extra speed
up since we only whitens non-zero cells.

>>>>

We used an off-the-shelf rendering engine that can create a realistic rendering and
a depth map. The CAD models we used contain color, texture and material information such as
transparency and reflectance to make the rendering as realistic
as possible to simulate the natural image statistics. An rendering example that we used in our experiments is
in Fig. \ref{fig:rendering}. Along with a rendering, we extracted a depth map which can later 
be used for reconstruction.

To handle intraclass variability, we used various CAD models (sedan, truck, racing car, hatchback etc) to cover intraclass variability and made renderings of these CAD models for various viewpoints. The
CAD models were cached so that when we fine-tune 2D-3D matching, we can render the model instantaneously.
Our renderer can continuously vary yaw, pitch, roll and the focal length as well so that the final fine tuning stage produces accurate the continuous viewpoint, a focal length and a bounding box.

@@

\subsection{Whitened Histograms of Orientations (WHO)}
\label{sec:who}
Our technique for rendering and generating exemplar template detectors on-the-fly
is drawing from recent work. Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
\cite{Hariharan12}, which uses feature statistics from natural images to whiten HOG
templates, making them more discriminative. Whitening is a common signal
processing operation for decorrelating a set of random variables
\cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
$k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
whitening the signal,

\begin{equation}
\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X]) \label{eq:whitening},
\end{equation}

we remove 2nd order correlation between all features. Since collecting covariance
matrix for every template shape is expensive, \cite{Hariharan12} proposed an easy
way to synthesize
covariance $\Sigma$ from autocovariance $\Gamma$ and we followed their
method to generate $\Sigma$.

@@

NZ-WHO removes these artifacts so that the background has no effect on the
template response. Let a vectorized HOG features of a rendering image $x\in
\mathcal{R}^{nd}$ be $x=T_f(I_r)$ where $n$ is the number HOG cells and $d$ be
the dimension of HOG feature. We create a new vector $x'$ which contains only
the non-zero elements of $x$. To be specific, let $I_d\in \mathcal{R}^{d\times
    d}$ be the identity matrix, $n'$ be the number of non-zero HOG cells, and a
matrix $S\in \mathcal{R}^{n'd \times nd}$ be the masking matrix that selects
non-zero HOG cell. For instance, a template has  $n=3, n'=2$, and only the
second HOG cell has $0$ norm, then

\begin{align}
S = \left[ \begin{array}{ccc}
        I_d & \mathbf{0} & \mathbf{0}\\
        \mathbf{0} & \mathbf{0} & I_d
        \end{array} \right]
\end{align}

Then, we can define $x' = S x, \mu' = S\mu, \Sigma' = S \Sigma S^T$.
After solving the resulting system (which is now smaller than
in the WHO approach) we find

\begin{equation}
w'=\Sigma'^{-1}(x' - \mu') \label{eq:nz-who},
\end{equation}

which we restore zero cells and reshape the vector into the final NZ-WHO
template that has the same dimension as the original HOG template.

@@

As a result, a GPU implementation of conjugate gradient converges in 80
ms when using 250 HOG cells, two orders of magnitude faster than the using
Cholesky factorization with Gaussian Elimination.

We report the real time analysis of whitening using decomposition and
conjugate gradient methods in Fig.~\ref{fig:whotime}. (a) compares the
absolute runtime of the different methods while (b) gives the obtained
speedup. We see that % We compare the speed of each of template generation methods in
% Fig.~\cite{fig:covariancetime_crop} Using naive Cholesky decomposition,
WHO template takes several seconds for realistic template sizes of
several hundred cells, while using the iterative Conjugate Gradient
method, it only takes 80ms. If we use NZ-WHO, we can gain extra speed
up since we only whitens non-zero cells.

### 2015-03-25 egpaper_final.tex
Added selector matrix $S$ that generates $x', \mu', \Sigma'$.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}
\graphicspath{ {figures/} }
% \cvprfinalcopy % *** Uncomment this line for the final submission

@@

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

>>>>

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}
\graphicspath{ {figures/} }
\cvprfinalcopy % *** Uncomment this line for the final submission

@@

\author{Christopher B. Choy, Michael Stark, Sam Corbett-Davies, Silvio Savarese\\
    Stanford University, Max Plank Institutes\\
    {\tt\small \{chrischoy, scorbett, stark, ssilvio\}@stanford.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}
